Toward single particle reconstruction without particle picking: Breaking the detection limit

### 2018-08-30 pnas/Towards.tex
New figures and small modifications

\begin{figure*}[h]
	\centering
	\begin{subfigure}[h]{0.24\textwidth}
		\centering
		\includegraphics[scale=0.35]{Einstien_progress_1}
		\caption{$5\times 10^2$ micrographs}
	\end{subfigure} 
	\begin{subfigure}[h]{0.24\textwidth}
	\centering
	\includegraphics[scale=0.35]{Einstien_progress_10}
	\caption{$5\times 10^3$ micrographs}
\end{subfigure} 
	\begin{subfigure}[h]{0.24\textwidth}
		\centering
		\includegraphics[scale=0.35]{Einstien_progress_100}
		\caption{$5\times 10^4$ micrographs}
	\end{subfigure} 
	\begin{subfigure}[h]{0.24\textwidth}
		\centering
		\includegraphics[scale=0.35]{Einstien_progress_246}
		\caption{$500\times 246$ micrographs}
	\end{subfigure}
	\caption{\label{fig:Einst_example} Recovery of Einstein from micrographs at noise level $\sigma = 3$ (see Figure~\ref{fig:micro_example}(c)). Averaged autocorrelations of the micrographs allow to estimate the power spectrum of the target image. This does not require particle picking. A phase retrieval algorithm (RRR) produces the estimates here shown, initialized randomly. Estimates are obtained from $5\times 10^2,5\times 10^3,5\times 10^4$ micrographs (growing across panels), each containing $700$ image occurrences on average. \TODO{XP is still running}}	
\end{figure*}

@@

\begin{figure}[h]
	\centering
\begin{subfigure}[h]{0.23\textwidth}
	\centering
	\includegraphics[scale=0.33]{Einstein_ps_error}
	\caption{relative power spectrum estimation error}
\end{subfigure} 
\begin{subfigure}[h]{0.23\textwidth}
	\centering
	\includegraphics[scale=0.33]{Einstein_recovery_error}
	\caption{relative recovery error}
\end{subfigure} 
	\caption{\label{fig:error_per_micro} Error curves for the experiment of Figure~\ref{fig:Einst_example} \TODO{XP is still running}}
\end{figure}

@@

We now analyze the third-order autocorrelation. Let us fix $\ell_1\geq\ell_2\ge0$. We have:
%
\begin{align}
%
&a_y^3[\ell_1,\ell_2] 
= \frac{1}{N}\sum_{i=0}^{N-1-\ell_1} y[i]y[i+\ell_1]y[i+\ell_2]
\nonumber \\
%
=& \underbrace{ \frac{ML}{N}\frac{1}{M}\sum_{j=1}^M 
	\frac{1}{L}\sum_{i=0}^{L-1-\ell_1}x[i]x[i+\ell_1]x[i+\ell_2]   }_{(1)}
\\& + \underbrace{\frac{1}{N}\sum_{i=0}^{N-1-\ell_1} \ep[i]\ep[i+\ell_1]\ep[i+\ell_2]}_{(2)}
\nonumber \\
&+ \underbrace{\frac{1}{N}\sum_{j=1}^{M} 
	\sum_{i=0}^{L-1} x[i]\ep[s_j + i+\ell_1]\ep[s_j+ i+\ell_2]}_{(3)}
\\& + \underbrace{\frac{1}{N}\sum_{j=1}^{M} 
	\sum_{i=0}^{L-1} \ep[s_j+i-\ell_1]x[i]\ep[s_j+ i+\ell_2-\ell_1]}_{(4)}
\nonumber \\
&+ \underbrace{\frac{1}{N}\sum_{j=1}^{M} 
	\sum_{i=0}^{L-1} \ep[s_j+i-\ell_2]\ep[s_j+i+\ell_1-\ell_2]x[i]}_{(5)}
\\ & + \underbrace{\frac{1}{N}\sum_{j=1}^{M} 
	\sum_{i=0}^{L-\ell_1+\ell_2-1} \ep[s_j+i]x[i+\ell_1-\ell_2]x[i]}_{(6)}
\nonumber \\
&+ \underbrace{\frac{1}{N}\sum_{j=1}^{M} 
	\sum_{i=0}^{L-\ell_2-1} x[i]\ep[s_j + i+\ell_1]x[s_j+ i+\ell_2]}_{(7)}
\\ & + \underbrace{\frac{1}{N}\sum_{j=1}^{M} 
	\sum_{i=0}^{L-\ell_1-1} x[i]x[i+\ell_1]\ep[s_j+ i+\ell_2]}_{(8)}.
%
\end{align}
%
Terms (6), (7) and (8) are linear in $\ep$, and can easily be shown to converge to 0 almost surely by the law of large numbers, by similar arguments as used previously. Term (1) converges to $\gamma a_x^3[\ell_1,\ell_2]$ almost surely, for the same reasons as~\eqref{eq:2nd_moment_signal_term}. To deal with terms (2)--(5), we must distinguish between different values of $\ell_1$ and $\ell_2$.

@@

>>>>

\begin{figure*}[h]
	\centering
	\begin{subfigure}[h]{0.24\textwidth}
		\centering
		\includegraphics[scale=0.35]{Einstien_progress_1}
		\caption{$500$ micrographs}
	\end{subfigure} 
	\begin{subfigure}[h]{0.24\textwidth}
	\centering
	\includegraphics[scale=0.35]{Einstien_progress_4}
	\caption{$2\times 10^3$ micrographs}
\end{subfigure} 
	\begin{subfigure}[h]{0.24\textwidth}
		\centering
		\includegraphics[scale=0.35]{Einstien_progress_40}
		\caption{$2\times 10^4$ micrographs}
	\end{subfigure} 
	\begin{subfigure}[h]{0.24\textwidth}
		\centering
		\includegraphics[scale=0.35]{Einstien_progress_400}
		\caption{$2\times 10^5$ micrographs}
	\end{subfigure}
	\caption{\label{fig:Einst_example} Recovery of Einstein from micrographs at noise level $\sigma = 3$ (see Figure~\ref{fig:micro_example}(c)). Averaged autocorrelations of the micrographs allow to estimate the power spectrum of the target image. This does not require particle picking. A phase retrieval algorithm (RRR) produces the estimates here shown, initialized randomly. Estimates are obtained from $500,2\times 10^3,2\times 10^4,2\times 10^5$ micrographs (growing across panels), each containing $700$ image occurrences on average. \TODO{XP is still running}}	
\end{figure*}

@@

\begin{figure}[h]
	\centering
	\includegraphics[scale=0.28]{Einstein_recovery_error_combined}
	\caption{\label{fig:error_per_micro}Relative error curves for the experiment of Figure~\ref{fig:Einst_example}.}
\end{figure}

%\begin{figure}[h]
%	\centering
%\begin{subfigure}[h]{0.25\textwidth}
%	\centering
%	\includegraphics[scale=0.33]{Einstein_ps_error}
%	\caption{relative power spectrum estimation error}
%\end{subfigure} 
%\begin{subfigure}[h]{0.25\textwidth}
%	\centering
%	\includegraphics[scale=0.33]{Einstein_recovery_error}
%	\caption{relative recovery error}
%\end{subfigure} 
%	\caption{\label{fig:error_per_micro} Error curves for the experiment of Figure~\ref{fig:Einst_example}}
%\end{figure}

@@

We now analyze the third-order autocorrelation. Let us fix $\ell_1\geq\ell_2\ge0$. We have:
%
\begin{align*}
%
&a_y^3[\ell_1,\ell_2] 
= \frac{1}{N}\sum_{i=0}^{N-1-\ell_1} y[i]y[i+\ell_1]y[i+\ell_2]
\nonumber \\
%
=& \underbrace{ \frac{ML}{N}\frac{1}{M}\sum_{j=1}^M 
	\frac{1}{L}\sum_{i=0}^{L-1-\ell_1}x[i]x[i+\ell_1]x[i+\ell_2]   }_{(1)}
\\& + \underbrace{\frac{1}{N}\sum_{i=0}^{N-1-\ell_1} \ep[i]\ep[i+\ell_1]\ep[i+\ell_2]}_{(2)}
\nonumber \\
&+ \underbrace{\frac{1}{N}\sum_{j=1}^{M} 
	\sum_{i=0}^{L-1} x[i]\ep[s_j + i+\ell_1]\ep[s_j+ i+\ell_2]}_{(3)}
\\& + \underbrace{\frac{1}{N}\sum_{j=1}^{M} 
	\sum_{i=0}^{L-1} \ep[s_j+i-\ell_1]x[i]\ep[s_j+ i+\ell_2-\ell_1]}_{(4)}
\nonumber \\
&+ \underbrace{\frac{1}{N}\sum_{j=1}^{M} 
	\sum_{i=0}^{L-1} \ep[s_j+i-\ell_2]\ep[s_j+i+\ell_1-\ell_2]x[i]}_{(5)}
\\ & + \underbrace{\frac{1}{N}\sum_{j=1}^{M} 
	\sum_{i=0}^{L-\ell_1+\ell_2-1} \ep[s_j+i]x[i+\ell_1-\ell_2]x[i]}_{(6)}
\nonumber \\
&+ \underbrace{\frac{1}{N}\sum_{j=1}^{M} 
	\sum_{i=0}^{L-\ell_2-1} x[i]\ep[s_j + i+\ell_1]x[s_j+ i+\ell_2]}_{(7)}
\\ & + \underbrace{\frac{1}{N}\sum_{j=1}^{M} 
	\sum_{i=0}^{L-\ell_1-1} x[i]x[i+\ell_1]\ep[s_j+ i+\ell_2]}_{(8)}.
%
\end{align*}
%
Terms (6), (7) and (8) are linear in $\ep$, and can easily be shown to converge to 0 almost surely by the law of large numbers, by similar arguments as used previously. Term (1) converges to $\gamma a_x^3[\ell_1,\ell_2]$ almost surely, for the same reasons as~\eqref{eq:2nd_moment_signal_term}. To deal with terms (2)--(5), we must distinguish between different values of $\ell_1$ and $\ell_2$.

@@

%\
